The FAIRification of research in real-world evidence: A practical introduction to reproducible analytic workflows using Git and R

### 2023-06-30 manuscript/manuscript.qmd
included another useful reference

Transparency and reproducibility in conducting real-world evidence (RWE) studies are critical scientific requirements for meaningful research. While many advances have been made in the documentation and reporting of study protocols and results[@wang2021; @schneeweiss2019; @berger2017; @wang2022], the transparency around the actual implementation and analytic steps is still significantly lacking, especially when analyses are implemented via line coding in statistical programming languages like R[@RCore2023] or Python. Although in other quantitative disciplines such as computational biology[@almugbel2017; @mammoliti2021; @russell2018] or health informatics[@bakken2019], the sharing of code is rather the rule than the exception, this practice is not as common in the (pharmaco-) epidemiological community.

>>>>

Transparency and reproducibility in conducting real-world evidence (RWE) studies are critical scientific requirements for meaningful research. While many advances have been made in the documentation and reporting of study protocols and results[@wang2021; @schneeweiss2019; @berger2017; @wang2022], the transparency around the actual implementation and analytic steps is still significantly lacking, especially when analyses are implemented via line coding in statistical programming languages like R[@RCore2023] or Python. Although in other quantitative disciplines such as computational biology[@almugbel2017; @mammoliti2021; @russell2018;@perez-riverol2016] or health informatics[@bakken2019], the sharing of code is rather the rule than the exception, this practice is not as common in the (pharmaco-) epidemiological community.
